---
title: "Assignment 2--R"
author: "Sherri Abbott"
date: "February 1, 2019"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Control flow:  Airport statistics

If your code uses any libraries, load them here.
```{r}
library(readr)
```

a. Download the data set `airport.csv`.  Read it into R and display the first few lines of data.

```{r}
airport = read_csv("airport.csv")
```

This data set contains data on all 135 medium and large airports in the US in 1990.  

(Dataset:  "US Airport Statistics," submitted by Larry Winner, University of Florida.   Dataset obtained from the Journal of Statistics Education (http://www.amstat.org/publications/jse). Accessed 3 June 2015. Used by permission of author.) 

b. **Use control flow** to print a list of airports at which the number of scheduled departures was less than the number of departures performed.

- The point of this assignment is to demonstrate your understanding of control flow, so please use control flow to solve this problem.

```{r}
numRows = dim(airport)[1]
for(ap_index in 1:numRows){ #iterate over airports
  if(airport$`Scheduled Departures`[ap_index] < airport$`Performed Departures`[ap_index]){ #check if scheduled departures is less than actual departures
    print(airport$Airport[ap_index])
  } #end of iteration over airports
} #end "check departures"
```

c. **Use control flow** to find the average (mean) number of passengers on flights from all the airports in part b.

- Your result should be 1 number:  The total number of passengers from all of the specified airports, divided by the total number of performed departures from all of the specified airports.

- The point of this assignment is to demonstrate your understanding of control flow, so please use control flow to solve this problem.

```{r}
num_pass = 0
num_dep = 0
numRows = dim(airport)[1]
for (ap_index in 1:numRows){ #iterate over airports
  if(airport$`Scheduled Departures`[ap_index] < airport$`Performed Departures`[ap_index]){ #check scheduled departures that are less than performed departures
   num_pass = num_pass + airport$Passengers[ap_index] #assign number of passengers to vector
     num_dep = num_dep + airport$`Performed Departures`[ap_index] #assign number of performed departures to vector
   } #end of iteration over airports
      } #end "check departures"
num_pass/num_dep
```

d.  Optional: 	If you know a more efficient way to do parts b and c in R, that's great!  Do that here and use the result to check your work.  (If you don't know a more efficient way, that's fine.  We'll discuss methods of writing efficient code later in the course.)
```{r}

```

-	Submit your .Rmd file and knitted .pdf or .docx file (.pdf preferred) to GitHub.
